\section{Branch and Bound for Vertex Cover}
\begin{frame}{General Algorithm}

  \begin{enumerate}
    \item Maintain the current cost and the current best solution.
    \item Extract $S_0, S_1$ and $S_{1/2}$ from an extreme solution of (LP).
    \item If adding $S_1$ exceeds the current best solution, stop (prune this branch).
    \item If $S_{1/2}$ is empty, update the current best solution if necessary and stop.
    \item Choose a vertex $v \in S_{1/2}$.
    \item Return to step 2 two following graphs in some order:
          \begin{itemize}
            \item Graph with $v$ included in the vertex cover (remove $v$ and its incident edges).
            \item Graph with $v$ excluded from the vertex cover (remove $v$'s neighbors and their incident edges, add $v$ to the current cost).
          \end{itemize}
  \end{enumerate}

  Different strategies for steps 5 and 6 lead to different algorithms.
\end{frame}

\begin{frame}{Experiments}
  We consider three strategies
  \begin{itemize}
    \item Choosing the vertex with the highest degree in $S_{1/2}$ and include it first.
    \item Choosing the vertex with the lowest degree in $S_{1/2}$ and exclude it first.
    \item Fully-strong branching \footnote{Bénichou, Michel, et al. "Experiments in mixed-integer linear programming." Mathematical programming 1.1 (1971): 76-94.}: choose the vertex and the order whose resulting two LP relaxations have the highest total value.
  \end{itemize}
\end{frame}

\begin{frame}{Results - Strategy 1: Highest Degree Include First}
  \small
  \begin{table}
    \centering
    \begin{tabular}{lrrrrrr}
      \hline
      Instance           & $|V|$ & $|E|$ & Opt VC & BnB Nodes & LP Calls & Time (s) \\
      \hline
      johnson8-2-4       & 28    & 210   & 21     & 31        & 31       & 0.22     \\
      MANN-a9            & 45    & 918   & 42     & 79        & 57       & 0.64     \\
      hamming6-2         & 64    & 1824  & 62     & 265       & 189      & 1.92     \\
      johnson8-4-4       & 70    & 1855  & 65     & 323       & 276      & 2.64     \\
      johnson16-2-4      & 120   & 5460  & 105    & 183       & 183      & 8.87     \\
      C125-9             & 125   & 6963  & 121    & 487       & 364      & 11.31    \\
      eco-foodweb-baywet & 128   & 2075  & 86     & 91        & 89       & 2.24     \\
      keller4            & 171   & 9435  & 156    & 2849      & 2835     & 47.41    \\
      brock200-1         & 200   & 14834 & 194    & 6723      & 6701     & 92.82    \\
      bn-macaque         & 242   & 3054  & 150    & 1851      & 1851     & 48.13    \\
      inf-USAir97        & 332   & 2126  & 149    & 791       & 775      & 6.37     \\
      delaunay\_n10      & 1024  & 3056  & 717*   & 96158     & 88318    & 600.04   \\
      econ-mahindas      & 1258  & 7619  & 730*   & 8270      & 8219     & 600.12   \\
      inf-euroroad       & 1174  & 1417  & 571*   & 66220     & 64256    & 600.01   \\
      mk11-b2            & 6930  & 20779 & 909    & 1         & 1        & 1.21     \\
      \hline
    \end{tabular}
  \end{table}
  \vspace{-0.2cm}
  {\footnotesize * indicates timeout (10 min limit)}
\end{frame}